Title

### 2017-11-29 Latex/MacroLunch_Dec2017/macrolunch_dec2017.tex
kept going with the presentation

%%%%%%% Slide %%%%%%
\begin{frame}
\frametitle{Identified Shocks}

@@

%%%%%%% Slide %%%%%%
\begin{frame}
\frametitle{Additional Restriction}

\begin{itemize}
	\item We rely in simple demand ans supply theory
	\begin{enumerate}
		\item 
		\item 
	\end{enumerate}

@@

	\item 
	\begin{enumerate}
		\item 
		\item 
	\end{enumerate}

@@

	\item 
	\begin{itemize}
		\item 
	\end{itemize}
\end{itemize}

@@

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{Identification strategy}

@@

    \begin{enumerate}
    	\item The news shock $V_{t-k}$ maximizes the FEV of future TFP subject to the restriction that it has no effect on the relative price $RP$ in the long run;

@@

    \item The tech shock $\varepsilon_t$ is considered as a residual shock and is left unrestricted.
   \end{enumerate}

>>>>

%%%%%%% Slide %%%%%%
\begin{frame}
\frametitle{Identified shocks}

@@

%%%%%%% Slide %%%%%%
\begin{frame}
\frametitle{Additional restriction}

\begin{itemize}
	\item We rely on simple demand and supply theory

@@

	\begin{enumerate}
		\item The IT shock is a \emph{sectoral} shock $\rightarrow$ we expect it to move relative prices
		\item The news shock is \emph{not} a sectoral shock $\rightarrow$ we have no a priori sense of what it should do to relative prices on impact, but after some time relative prices should go back to their initial value
	\end{enumerate}

@@

	$\rightarrow$ add the restriction that a news shock should have no effect on relative prices after a reasonable time

\hspace{4cm} $\hookrightarrow$ enough for prices to adjust, so

\hspace{4cm}   between 6 -12 quarters

@@

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{Identification strategy overall}

@@

    \begin{enumerate}
    	\item The news shock $V_{t-k}$ maximizes the FEV of future TFP subject to the restriction that it has no effect on the relative price $RP$ at a small number of quarters;

@@

    \item The tech shock $\varepsilon_t$ is considered as a residual shock and is left unrestricted (unidentified).
   \end{enumerate}

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{Our favorite specification}

	\begin{itemize}
	\item Recall: dataset is quarterly and covers 1989:q1-2017-q1.

	\item One lag (as suggested by BIC and HQ).

	\item Horizon of FEV-maximization: 100 quarters.

	\item Restriction on relative prices after a news shock is imposed at 8 quarters.

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{Results - Impulse responses to a news shock}

\includegraphics[scale=0.5]{}

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{Results - Impulse responses to an IT shock}

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{Results - FEV of TFP explained by the two shocks}

    \hspace{2.25cm}
\begin{large}
	\begin{tabular}{lccc}
	\hline
		& News & IT & Total \\
		\hline
		 & 0.37195 & 0.43944 & 0.81138 \\
		\hline
	\end{tabular}
\end{large}
